From Active Hostilities to Frozen Stalemates: Assessing the Role of External Support in Civil Conflict Dynamics

### 2023-10-30 paper.qmd
Rename fc package to fc.utils
Avoid potential clashes with CRAN packages
Use modelsummary for regression tables

---
title: When Civil Conflicts Freeze
author: J.L.A. Krusell
date: "`r Sys.Date()`"
linestretch: 1.25
bibliography: library.bib
format: pdf
execute:
    echo: false
    warning: false
---

```{r setup, include = F}
library(bayesplot)
library(dplyr)
library(ggplot2)
library(ggthemes)
library(knitr)

@@

@@

```{r}
fit <- readRDS("./posteriors/probit.rds")

fit$draws("delta") |> mcmc_areas() +
    scale_y_discrete(labels = c("delta[1]" = "Ext. Sup. to Gov",
                                "delta[2]" = "Ext. Sup. to Rebel",
                                "delta[3]" = "Interaction"))
```

@@

>>>>

---
title: "From Active Hostilities to Frozen Stalemates: Assessing the Role of External Support in Civil Conflict Dynamics"
author: J.L.A. Krusell
date: "`r Sys.Date()`"
linestretch: 1.25
bibliography: library.bib
format: pdf
execute:
    echo: false
    warning: false
---

[//]: # Setup R environment
```{r setup, include = F}
library(dplyr)
library(ggplot2)
library(ggthemes)
library(ggdist)
library(modelsummary)
library(kableExtra)
library(knitr)
library(patchwork)
library(tidyr)

# Project specific utility package
library(fc.utils)

@@

Descriptive statistics split between positive and negative outcomes

@@

```{r}
#| fig.cap: Posterior estimates for \delta from a single variate probit model
fit <- readRDS("./posteriors/frozen-bin-all/fit.rds")

delta <- fit$draws("delta", format = "df") |>
    select(matches("delta")) |>
    pivot_longer(everything(), names_to = "variable")

ggplot(delta, aes(x = value, y = variable, fill = variable)) +
    stat_halfeye(alpha = 0.8, show.legend = F) +
    geom_vline(xintercept = 0, linetype = "dashed", alpha = 0.2) +
    theme(axis.title.x = element_blank(),
          axis.title.y = element_blank()) +
    scale_y_discrete(labels = c("delta[1]" = "Ext. Sup. to Gov",
                                "delta[2]" = "Ext. Sup. to Rebel",
                                "delta[3]" = "Interaction"))
```

```{r}
#| fig.cap: Average marginal effects for the three treatment conditions on the predicted probability of a frozen conflict onset.[^ame]
ame <- fit$draws("ame", format = "df") |>
    select(matches("ame")) |>
    pivot_longer(everything(), names_to = "variable")

ggplot(ame, aes(x = value, y = variable, fill = variable)) +
    stat_eye(alpha = 0.8, show.legend = F) +
    geom_vline(xintercept = 0, linetype = "dashed", alpha = 0.2) +
    theme(axis.title.x = element_blank()) +
    labs(x = parse(text = "bold('AME '*Delta)")) +
    scale_y_discrete(labels = c("ame[1]" = "Ext. Sup. Gov Only",
                                "ame[2]" = "Ext. Sup. Rebel Only",
                                "ame[3]" = "Ext. Sup. to Both")) +
    coord_flip()
```

[^ame]: Hello World

@@

::: {#refs}
:::

# Appendix

## Robust Checks

### Observational Probit Models

```{R}
models <- list.dirs("posteriors", recursive = F)
stopifnot(length(models) != 0)

fits <- lapply(models, \(dir) file.path(dir, "fit.rds") |> readRDS())
names(fits) <- basename(models)
```

```{R}
#| fig-height: 7
summary.df <- lapply(fits, function(fit) {
    post <- post_summarise(fit, "delta", rename = T, model_info = T,
                           probs = c(0.025, 0.17, 0.5, 0.83, 0.975)) |>
        rename(median = `50%`,
               lower95 = `2.5%`,
               upper95 = `97.5%`,
               lower66 = `17%`,
               upper66 = `83%`)
}) |> bind_rows()

summary.df$variable <- sub("_(prop|bin.*)$", "", summary.df$variable)

ggplot(summary.df, aes(treatment_aggregation, median, color = outcome)) +
    geom_point(size = 1.5, position = position_dodge(width = 0.25)) +
    geom_errorbar(aes(ymin = lower95, ymax = upper95), position = position_dodge(0.25), width = 0) +
    geom_errorbar(aes(ymin = lower66, ymax = upper66), position = position_dodge(0.25), linewidth = 1.25, width = 0) +
    geom_hline(yintercept = 0, linetype = "dashed", alpha = 0.2) +
    facet_grid(variable ~ episodes)

```

```{R}
models <- list.dirs("posteriors", recursive = F)
stopifnot(length(models) != 0)

fits <- lapply(models, \(dir) file.path(dir, "fit.rds") |> readRDS())

frozen <- fits[grepl("/frozen", models)]
strict_frozen <- fits[grepl("/strict_frozen", models)]

modelsummary(frozen, pars = c("alpha", "delta", "beta"),
             statistic = "conf.int", title = "Frozen Conflicts") |>
    add_header_above(c(" " = 1, "All Episodes" = 3, "High Intensity Only" = 3)) |>
    kable_styling(font_size = 8, full_width = F) |>
    landscape()
```

```{R}
modelsummary(strict_frozen, pars = c("alpha", "delta", "beta"),
             statistic = "conf.int", title = "Frozen Conflicts Lasting >2 Years") |>
    add_header_above(c(" " = 1, "All Episodes" = 3, "High Intensity Only" = 3)) |>
    kable_styling(font_size = 8, full_width = F) |>
    landscape()
```
